### 2019-10-30 paper/3_3_generalizing_the_dantzig_selector_bound.tex
Finish 3.3

= \NC \R {2 \log N_h} \NR

@@

\DispNum {--;g1,g1;} {

@@

Let \m {\M {P}} be fixed, and instance of \m {\V {z}} be given.
Then

@@

\NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}}
\leq \NC  2 \R {\log N_h} \NR

@@

=\NC 1, \ldots, N_h. \NR

@@

holds with probability \m {\geq 1 -N_h^{-1}}.

@@

Indeed, recall the fact that \m {\M {P} \DB {:, n_g}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}, the quantity \m {\Nm {\IP {\V {z} , \M {P} \DB {:, n_h}}}} observes standard Normal.
Recall the following bound for \m {Q} function
\NC Q\SB {x}
\leq \NC \F {1} {2} \Ss {e}^{-x^2/2} \NR
Particularly, for \m {x =\R {2 \log N_h}},

@@

\NC Q\SB {\R {2 \log N_h}}
=\NC \F {1} {N_h}. \NR

@@

\leq \NC  4 \R {\log N_h} \NR

@@

holds with probability \m {\geq 1 -N_h^{-1}}.

@@

\NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} \DB {:,n_y}}
= \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} \DB {:,n_y}} \NR

@@

\NC = \NC \IP {\M {P} \V {d}, \M {P} \DB {:,n_y}} \NR

@@

\NC \VNm {\M {P} \DB {:,n_y}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty

@@

\NC \leq \NC 2\R {\log N_h} \NR

@@

By triangle inequality, together with \Rf {E-h-2N-Nh}, we have

@@

\NC \VNm {\M {P} \DB {:,n_y}^\Adj \M {P} \V {d}} _\infty
\leq \NC \VNm {\IP {\V {z}, \M {P} \DB {:,n_y}}} _\infty
+\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} \DB {:,n_y}} \NR

@@

\NC \leq \NC 2 \R {\log N_h} +2 \R {\log N_h} \NR
which implies
\DispNum {P-d-4l-Nh} {
\leq \NC 4 \R {\log N_h}. \NR

@@

@@

\leq \NC \VNm {\V {d} _{\MC {A} \MC {B}}} _2^2 +\F {1} {S} \VNm {\V {d} _{\SB{\MC {C}}}} _1^2 \NR

@@

The other one reads

@@

\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2

@@

\NC \leq \NC \RB {1 +\d _{s}} \RB {\VNm {\V {x}_1} +\VNm {\V {x}_2}} \NR

@@

\NC \leq \NC \RB {1 +\d _{s}} \D \R{2} \VNm {\V {x}_1 +\V {x}_2} \NR

@@

\NC \d_{2s}
\leq \NC \R {2} \d_{s} \NR

@@

If \m {\M {Q}'} has \m {\d}-RIP, then, for \m {M=1,2,3,\dots} so that \m {\d _{Ms}} is meaningful,

@@

\NC \d_{Ms}
\leq \NC \R {M} \d_{s} \NR

@@

Thus we have, in view of \Rf {d-2-11-C1},

@@

\leq \NC \F {1} {1-\R{2} \d_{S}} \VNm {P _{\MC {A} \MC {B}}^\Tr P d} _2

@@

We are going to combine previous lemmata and show the main result.
For simplicity, set
%
\DispNum {d'-S;18,18;} {
\NC \d_S
\leq \NC \F {1} {8} \NR
}
%
Thus
\DispNum {S-S-4N-NH} {
\NC S
=\NC L \log N_H \NR
}
%
\Result
{Theorem}
{
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then the bound
%
\DispNum {d-2-42-NH} {
\NC \VNm {\V {d}} _2
\leq \NC 4 \R {2L} \log N_H \NR
}
}
%

We start to prove \Rf {d-2-42-NH}.
By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P-d-4N-Nh},
%
\DispNum {P-2-PP-NH} {
\NC \VNm {\M {P} _{\MC {A} \MC {B}}^\Tr \M {P} \V {d}} _2
\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
%
\NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
%
\NC \leq \NC 4 \R {2 \log N_H} \NR
}
%
By \m {\ell_p}-norm inequality, by the definition of truncation, by \Rf {d-2-11-C1}, and by \Rf {P-2-PP-NH} just above,
%
\Disp {
\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
\leq \NC \R {S} \VNm {\V {d} _{\SB{\MC {A}}}} _2 \NR
%
\NC \leq \NC \R {S} \VNm {\V {d} _{\SB{\MC {AB}}}} _2 \NR
%
\NC \leq \NC 4 \R {2 \log N_H}
+\F {1} {\R{L \log N_H}} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
}
%
Next, we want to use \Rf {d-1-dA-C1} to eliminate \m {\VNm {d _{\SB{\MC {A}}}} _1}.
%
\DispNum {8,2,nn-hh;} {
\NC \leq \NC 4 \R {2 \log N_H}
+\F {1} {\R{L \log N_H}} \RB {\VNm {\V {d} _{\SB{\MC {A}}}} _1 +2\VNm {\V {g} _{\SB{\MC {C}}}} _1} \NR
}
%
And \Rf {a-2-4N-NH} gives, after arrangement,
%
\DispNum {d-A;8,2;} {
\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
\leq \NC 4 \R {2 \log N_H}
+2\VNm {\V {g} _{\SB{\MC {C}}}} _1 \NR
%
\NC \leq \NC \RB {16 \R {2} +\F {4} {\pi^2} \R {1 -\F {2} {\pi}}} \log N_H \NR
}
%
We are now in a position to bound \m {\VNm {d} _2^2}.
Using \Rf {d-2-dA-12} again, we have
%
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC 32 S \log N_H
+8 \d_{3S} \R {2 \log N_H} 
+\F {\d_{3S}^2} {S} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
}
%
Finally, plug in the bound for \m {\VNm {\V {d} _{\SB{\MC {C}}}} _1}, the last unknown, and we make use of the almost-sparsity condition of \m {\VNm {\V {d} _{\SB{\MC {C}}}} _1}.
Again for simplicity, we keep only the first order small terms.
%
\Disp {
\NC \VNm {\V {d}} _2^2
\leq \NC 32 S \log N_H
+\F {8 \R {2\pi}} {3} \d_{3S} L \R {\F {\log N_H} {N_H}}
+\F {\pi} {9} \F {L} {s^2 N_H} \NR
}
%
Set \m {\d_S =1} for the worst situation, and we get the desired bound.

In addition to the bound, we shall discuss the four sources of error, namely
\DispNum {q-q-2q-ar} {
\NC q
\simeq \NC 2 \RB {q _{\Rm {isom}, B} + q _{\Rm {isom}, R}} +q _{\Rm {nois}} +q _{\Rm {spar}} \NR
}
subscript for restricted isometry, noise, sparsity, respectively.

Quoting previous results, they are
\Disp {
q
\simeq \Ss {e} ^{N_B \d}
}
%
Provided the design values
\Disp {
\NC N_R
\leftarrow \NC \RB {\log N_H} ^{3/2} \NR
%
\NC N_B
\leftarrow \NC \log \log N_H \NR
}
%
And we get the estimation
\Disp {
\NC q
=\NC \MC {O} \SB {\F {1} {\RB {\log N_H}^3}} \NR
}
%
\stopsubsection
\stopsection

>>>>

= \NC \R {4 \log N_H} \NR

@@

@@

To prove the next result, fix an instance of \m {\M {P}} and instance of \m {\V {z}}.
We claim that

@@

\NC \MB {E} \SB {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}}
\leq \NC  2 \R {2 \log N_H} \NR

@@

=\NC 1, \ldots, N_H^2. \NR

@@

This follows by the fact that \m {\M {P} _{\SB {:, n_g}}} has unity \m {\ell_2}-norm, and on the randomness of \m {\V {z}}, the quantity \m {\Nm {\IP {\V {z} , \M {P} _{\SB {:, n_h}}}}} observes Standard Normal.
To bound the failure probability, recall the tail bound for \m {Q} function
\NC Q\SB {x'}
\leq \NC \F {1} {2} \Ss {e}^{-x'^2 /2} \NR

@@

Particularly, for \m {x' =\R {4 \log N_H}}, this gives the failure probability

@@

\NC Q\SB {\R {4 \log N_H}}
=\NC \F {1} {N_H^2}. \NR

@@

\leq \NC  4 \R {2 \log N_H} \NR

@@

holds for probability \m {p} 
\DispNum {1-p-NH-H2} {
\NC 1 -p
\leq \NC N_H^{-2}. \NR

@@

\NC \IP {\V {z} -\RB {\V {y} -\M {P} \hat {\V {g}}}, \M {P} _{\SB {:,n_y}}}
= \NC \IP {\M {P} \hat {\V {g}} -\M {P} \V {g}, \M {P} _{\SB {:,n_y}}} \NR

@@

\NC = \NC \IP {\M {P} \V {d}, \M {P} _{\SB {:,n_y}}} \NR

@@

\NC \VNm {\M {P} _{\SB {:,n_y}}^\Adj \RB {\V {y} -\M {P} \hat {\V {g}}}} _\infty

@@

\NC \leq \NC 2\R {2 \log N_H} \NR

@@

By triangle inequality, together with \Rf {Q-h-1N-Nh}, we obtain the desired result.

@@

\NC \VNm {\M {P} _{\SB {:,n_y}}^\Adj \M {P} \V {d}} _\infty
\leq \NC \VNm {\IP {\V {z}, \M {P} _{\SB {:,n_y}}}} _\infty
+\IP {\V {y} -\M {P} \hat {\V {g}}, \M {P} _{\SB {:,n_y}}} \NR

@@

\NC \leq \NC 2 \R {2 \log N_H} +2 \R {2 \log N_H} \NR

@@

One of them reads
\leq \NC \VNm {\V {d} _{\SB {\MC {AB}}}} _2^2 +\F {1} {S} \VNm {\V {d} _{\SB{\MC {C}}}} _1^2 \NR
By power mean inequality, we get a statement cruder than \Rf {d-2-dA-12} that

@@

\DispNum {d-2-dA-C1} {
\NC \VNm {\V {d}} _2
\leq \NC \VNm {\V {d} _{\SB {\MC {AB}}}} _2 +\F {1} {\R {S}} \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR

@@

The other one of them reads

@@

\leq \NC \F {1} {1-\d_{2S}} \VNm {P _{\SB {\MC {AB}}}^\Tr P d} _2

@@

\NC \leq \NC \RB {1 +\d _{s'}} \RB {\VNm {\V {x}_1} +\VNm {\V {x}_2}} \NR

@@

\NC \leq \NC \RB {1 +\d _{s'}} \D \R{2} \VNm {\V {x}_1 +\V {x}_2} \NR

@@

\NC \d_{2s'}
\leq \NC \R {2} \d_{s'} \NR

@@

If \m {\M {Q}'} has \m {\d_{s'}}-RIP, then, for \m {M=1,2,3,\dots} so that \m {\d _{Ms'}} is meaningful,

@@

\NC \d_{Ms'}
\leq \NC \R {M} \d_{s'} \NR

@@

In particular,
\DispNum {d'-S-Ll-d's} {
\NC \d_{S}
\leq \NC \R {L} \RB {\log N_H} ^{1/4} \d_{s} \NR
So \Rf {d-2-11-C1} becomes

@@

\leq \NC \F {1} {1-\R{2} \d_{S}} \VNm {P _{\SB {\MC {AB}}}^\Tr P d} _2

@@

We are going to combine previous lemmata and show the main result.
For simplicity, set
%
\DispNum {d'-S-18-18} {
\NC \d_S
\leq \NC \F {1} {8} \NR
}
%
Thus
\DispNum {S-S-4N-NH} {
\NC S
=\NC L \log N_H \NR
}
%
\Result
{Theorem}
{
Let \m {\V {y}}, \m {\M {P}}, \m {\V {g}}, \m {\hat {\V {g}}}, \m {\V {d}} be defined as above.
Then the bound
%
\DispNum {d-2-42-NH} {
\NC \VNm {\V {d}} _2
%
\leq \NC 3.29 \R {L} \log N_H +4.56 \R {L} \R {\log N_H}^3 \NR
}
%
holds for probability \m {p}, with
%
\DispNum {1-p-ON-13} {
\NC 1 -p
=\NC \MC {O} \SB {N_H ^{-1/3}} \NR
}
}

To prove \Rf {d-2-42-NH}, we simplify the expression for \m {\VNm {\V {d} _{\SB{\MC {AB}}}} _2} in \Rf {d-2-11-C1} and the one for \m {\VNm {\V {d} _{\SB{\MC {C}}}} _1} in \Rf {d-1-dA-C1} and 
In this section we substitute rough numbers.

By the definition of truncation, by \m {\ell_p} norm inequality, by \Rf {P-d-4N-Nh},
%
\DispNum {P-2-PP-NH} {
\NC \VNm {\M {P} _{\SB {\MC {AB}}}^\Tr \M {P} \V {d}} _2
\leq \NC \VNm {\M {P}^\Tr \M {P} \V {d}} _2 \NR
%
\NC \leq \NC \R {S} \VNm {\M {P}^\Tr \M {P} \V {d}} _\infty \NR
%
\NC \leq \NC 5.65 \R {\log N_H} \NR
}
%
By \m {\ell_p}-norm inequality, by the definition of truncation, by \Rf {d-2-11-C1}, and by \Rf {P-2-PP-NH} just above,
%
\Disp {
\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
\leq \NC \R {S} \VNm {\V {d} _{\SB{\MC {A}}}} _2 \NR
%
\NC \leq \NC \R {S} \VNm {\V {d} _{\SB{\MC {AB}}}} _2 \NR
%
\NC \leq \NC 1.21 L \R {\log N_H}^3
+0.262 \VNm {\V {d} _{\SB{\MC {C}}}} _1 \NR
}
%
And \Rf {a-2-4N-NH} gives, after arrangement,
%
\DispNum {d-A1-16-H2} {
\NC \VNm {\V {d} _{\SB{\MC {A}}}} _1
%
\leq \NC 1.64 L \R {\log N_H}^3 +0.951 L \RB {\log N_H}^2 \NR
}
%
Then, substituting \Rf {g-C-4p'-NH} and \Rf {d-A1-16-H2} above into \Rf {d-1-dA-C1}, we get
\DispNum {d-C1-16-H2} {
\NC \VNm {\V {d} _{\SB{\MC {C}}}} _1
%
\leq \NC 1.64 L \R {\log N_H}^3 +3.61 L \RB {\log N_H}^2 \NR
}
%
And \Rf {d-2-11-C1} becomes
%
\DispNum {d-2-16-H3} {
\NC \VNm {\V {d} _{\SB{\MC {AB}}}} _2
%
\leq \NC 1.64 \R {L} \log N_H +0.951 \R {L} \R {\log N_H}^3 \NR
}
We are now in a position to bound \m {\VNm {d} _2}, just by using \Rf {d-2-dA-C1} again, and plugging in \Rf {d-2-16-H3} and \Rf {d-C1-16-H2} above.

In addition, we shall discuss the four events of failure, namely
\DispNum {q-q-2q-ar} {
\NC q
\eqsim \NC 2 \RB {q _{\Rm {iso}, B} + q _{\Rm {iso}, R}} +q _{\Rm {no}} +q _{\Rm {sp}} \NR
}
subscript respectively for restricted isometry, noise, sparsity, respectively.
Quoting previous results \Rf {1-p-1N-H3}, \Rf {P-d-eN-d4}, \Rf {1-p-ex-d's}, and \Rf {1-p-NH-H2}, we make some approximation and set
\DispNum {q-B-2e-Lp'} {
\NC q _{\Rm {iso}, B}
\lesssim \NC 2 \Ss {e} ^{-N_B /12} \NR
%
\NC q _{\Rm {iso}, R}
\lesssim \NC 2 N_H ^{-1/3} \RB {\log N_H} ^{-1/6} \NR
%
\NC q _{\Rm {no}}
\lesssim \NC N_H ^{-2} \NR
%
\NC q _{\Rm {sp}}
\lesssim \NC 2 \Ss {e} ^{-9L/\pi} \NR
}
%
If we provide the design values
\DispNum {N-B-4l-H2} {
\NC N_B
\gtrsim \NC 4 \log N_H \NR
%
\NC N_R
\gtrsim \NC 16 L \RB {\log N_H}^2 \NR
}
%
It can be seen that
\DispNum {q-p-qn-oR} {
\NC q _{\Rm {sp}}
\lesssim \NC q _{\Rm {no}} \NR
%
\NC \lesssim \NC q _{\Rm {iso}, B} \NR
%
\NC \eqsim \NC q _{\Rm {iso}, R} \NR
}
%
then we get the estimation
\DispNum {q-q-ON-13} {
\NC q
\eqsim \NC q _{\Rm {iso}, R} \NR
%
\NC \eqsim \NC q _{\Rm {iso}, B} \NR
%
\NC \eqsim \NC 2 N_H ^{-1/3} \NR
}
%

%gC1 {g-C-4p'-NH}
%dC1 {d-1-dA-C1}
%PPd-infty {P-d-4N-Nh}
%d2 {d-2-dA-C1}
%dAB2 {d-2-11-C1}

\stopsubsection
\stopsection
